---
title: "HM 1"
author: "by Tamires Amorim"
date: "2/5/2021"
output:
 github_document
---

## Homework#1

1.loading main package
```{r}
library(ggplot2)
library(dplyr)
library(plotly)
library(purrr)
library(stringi)
library(stringr)
library(tidyverse)
library(DT)
```

## 3.2.4 Exercises


### 1.Run ggplot(data = mpg). What do you see?

That line of coding only shows a empty square with no content inside.Although, when I used the ggplot2::mpg, I was able to see the table with information of different vehicles, as manufacturer, model, engine size, fuel efficiency and so on. 
```{r}
ggplot2::mpg
```

### 2.How many rows are in mpg? How many columns?

There are 234 rows and 11 columns. 

### 3.What does the drv variable describe? Read the help for ?mpg to find out.
It means the the type of drive train, where f = front-wheel drive, r = rear wheel drive, 4 = 4wd.

### 4. Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))
```

### 5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
Because it not a clear representation of the relationship between the "type" of car and type of drive train, we cannot draw any conclusion from visualizing this graph. 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = drv))
```

## 3.3.1 Exercises

### 1. What’s gone wrong with this code? Why are the points not blue?
The coding bellow is wrong because it positioned the parentheses in the wrong place. It included the color blue as an object to be classified in the graph.  
```{r}
#ggplot(data = mpg) + 
#  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

The correct code to turn the points in the plot blue, will add the variables x and y separated from "color = blue" by using parentheses:
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

### 2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
The categorical variables are manufacturer, model, trans, drv, fl and class.
Continuous are displ, year, cyl, cty and hwy.  
The function glimpse() can show the variables.
```{r}
glimpse(mpg)
```



### 3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
When we map a categorical vs. continuous variables we get a warning message that "using size for a discrete variable is not advised". Meaning that changing size, transparency or shape in a graph of unordered variable to an ordered aesthetic will not convey a clear picture of the information we want to obtain from the graph, as observed. 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```

### 4. What happens if you map the same variable to multiple aesthetics?
Multiple aesthetics do not convey clear information, only one is enough to display the relationship between variables. 
```{r}
ggplot (mpg)+
geom_point(mapping=aes(x = displ, y = hwy, color =class, shape =class))
```

### 5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
The stroke aesthetics is used to modify the width of the border for shapes that have border.
```{r}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, colour = "black", fill = "white", size = 5, stroke = 5)
```

### 6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.
It classifies the values bellow 5 as true and everything greater than 5 false. 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))
```

## 3.5.1 Exercises

### 1. What happens if you facet on a continuous variable?
It does not display clear information. The faucet function works only for discrete variables. 
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  facet_grid(~ cty)
```

### 2. What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
The plot bellow shows the combination of the quadrants that contain information on the facet_grid, for instance, the quadrant 4 and 4 contains data, but the quadrant 4 and r does not. The same is true for all the other combinations in the facet-grid.  
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl))
```
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cty)) +
  facet_grid(drv ~ cyl)
```

### 3.What plots does the following code make? What does . do?
The dot is used to facet in different dimensions, the first showing the rows, values on the y-axis, and the second showing the columns, values on the x-axis.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ drv)
```

### 4.Take the first faceted plot in this section: 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

#### What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?
When comparing the faceting version with the color aesthetic, it is possible to observe how the information is more clearly presented in the faceted plot. As observed bellow, where we break down the content in different squares with its corresponding category. 
If the data was larger then the color aesthetic would be even more confusing, because the difference between colors would not be as evident. Color Aesthetic example:
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

### 5.Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?
To control the number of rows and columns we use nrow and ncol respectively. To change the order in which the panels appear, we can also "change the levels of the underlying factor" (R Documentation). In the facet_grid() we do not use nrow and ncol arguments because the number of the different variables will determine the number of rows and columns. 

### 6. When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?
For better visualization purposes. To display the information clearly, we add the variables with more unique levels in the horizontal. 

## 3.6.1 Exercises 

### 1. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
Line charts use geom_line(). Boxplot uses geom_boxplot(). Histograms geo_histogram() and area chart geom_area()

### 2,Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.
I predicted it would look like the scatter plot we ran above, but with the shade and line above it.And I got it wrong. 
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

### 3. What does show.legend = FALSE do? What happens if you remove it? Why do you think I used it earlier in the chapter?
The show legend displays the legend box, removing it or setting to =false will eliminate the legend box. Because there were three plots and adding a legend to one plot, would make it difficult to see the differences between the groups. 
```{r}
ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, colour = drv),
    show.legend = FALSE
  )
```

### 4.What does the se argument to geom_smooth() do?
Geo_smooth, use a single geometric object to display multiple rows of data. The se will add standard errors to the lines. 
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = TRUE)
```

### 5. Will these two graphs look different? Why/why not?
No. Because the code 2 will treat these mappings as global mappings that apply to each geom in the graph. Meaning that code 2, will produce the same plot as the previous code 1. This tool helps us avoid errors when typing codes like code 1 multiple times
```{r}
##CODE 1
ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

##CODE 2
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()
```

### 6. Recreate the R code necessary to generate the following graphs.
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(se = FALSE)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(group = drv), se = FALSE) +
  geom_point()

ggplot(mpg, aes(x = displ, y = hwy, colour = drv)) +
  geom_point() +
  geom_smooth(se = FALSE)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(colour = drv)) +
  geom_smooth(se = FALSE)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(colour = drv)) +
  geom_smooth(aes(linetype = drv), se = FALSE)

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 4, color = "white") +
  geom_point(aes(colour = drv))
```






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



